High-Efficiency, Small-Footprint Couplers Between Arbitrary Nanophotonic Waveguide Modes

### 2012-01-05 presentations/ob1_wg_paper/paper.tex
Finished bulk of editing on the ob-1 paper.

\begin{thebibliography}{99}
\bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
    ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
    nanophotonic circuits,''
    Opt. Lett. \textbf{35}, 1290-1292 (2010)
\bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
    ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
    Opt. Lett. \textbf{26}, 1888-1890 (2001)
\bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
    ``Active control of slow light on a chip with photonic crystal waveguides,''
    Nature \textbf{438}, 65-69 (2005)
\bibitem{slotfocus} M. Lipson, 
    ``Guiding, Modulating, and Emitting Light on 
    Silicon-Challenges and Opportunities,'' 
    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005) 
\bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
    D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
    C. Lagahe, and R. Baets, 
    ``Electrically pumped InP-based microdisk lasers integrated with a 
    nanophotonic silicon-on-insulator waveguide circuit,'' 
    Opt. Express \textbf{15}, 6744-6749 (2007) 
\bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
    D. S. Ly-Gagnon, K. C. Saraswat and D. A. B. Miller, 
    ``Nanometre-Scale Germanium Photodetector Enhanced by a 
    Near-Infrared Dipole Antenna,'' 
    Nature Photonics \textbf{2}, 226 – 229 (2008) 
\bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
    ``Nanotaper for compact mode conversion,'' 
    Opt. Lett. \textbf{28}, 1302-1304 (2003) 
\bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
    M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
    ``Adiabatic theorem and continuous coupled-mode theory for 
    efficient taper transitions in photonic crystals,''
    Phys. Rev. E \textbf{66}, 066608 (2002)
\bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
    ``Robust topology optimization of photonic crystal waveguides with 
    tailored dispersion properties.'' 
    J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
\bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
    \emph{Convex Optimization} 
    (Cambridge University Press, 2004)
\bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10570 (2011) 
\bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

% Why is waveguide mode conversion important?
Optical mode conversion, 
    the efficient transfer of photons from one guided mode to another,
    is a fundamental requirement in nanophotonics.
For instance, efficient conversion between waveguides modes
    is essential for:
    \begin{itemize}
        \item Coupling to and from optical fiber\cite{fibergrating}, 
        to communicate with the outside world.
    \item Coupling between various nanophotonic waveguides, 
        since different waveguides are best suited for different applications.
        For example, ridge waveguides seem ideal for 
            low-loss transport\cite{ridge},
            but other waveguides, 
            such as photonic crystal waveguides or slot waveguides,
            may be better suited for slow-light\cite{pcslow} 
            or nonlinear optical devices based on 
            localized field intensities\cite{slotfocus}.
    \item Coupling between different materials systems such as
       passive, active\cite{active}, and metallic\cite{metallic} devices. 
    \end{itemize}
In fact, the problem of converting between nanophotonic modes is essentially
    the function of all linear nanophotonic devices, since
    any linear device is completely characterized by its input and output modes.

In this paper, we propose a design algorithm which, 
    we believe, solves this problem.
Namely, we outline a method capable of designing nanophotonic devices
    to efficiently transfer photons between 
    arbitrary input and output modes,
    and we demonstrate this method by designing various nanophotonic couplers
    between different waveguides.

Furthermore, we show that our method 
     does not employ brute-force parameter searches;
     does not require a good initial design;
     is computationally fast (no simulations required);
     and can generate high efficiency couplers within a very small footprint. 
% 
% 
% % Why are current solutions insufficient?
% % Brute force
% Of the design strategies currently available,
%     brute-force parameter search is the most often employed 
%     because of its sheer simplicity.
% Although it may be suitable for tuning existing designs,
%     the parameter space for most practical devices is simply too large
%     for such a strategy to be tractable.
% 
% % Adiabatic mode conversion (large devices, symmetry breaking)
% Adiabatic mode conversion strategies have been succesful
%     for certain fiber-waveguide\cite{fwadia} and 
%     waveguide-waveguide\cite{wwadia} couplers,
%     even if the resulting devices often require large footprints.
% However, adiabatic approaches cannot be used in many important cases 
%     such as coupling in the out-of-plane direction, or
%     coupling between modes of opposite symmetry.

% How does your algorithm solve this problem?
% \subsection{Advantages of objective-first design}
\section{Objective-first formulation}
% What is objective-first optimization?
The typical approach to designing physical structures can be formulated 
    in the following way:
    \begin{subequations}\label{eq:adj}
    \begin{align} 
    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
    \end{align}
    \end{subequations}
    where $x$ is the field variable and $p$ is the structure variable.
Here, $f(x)$, the \emph{design objective}, 
    calculates the performance of the device 
    (e.g. amount of power not coupled to output mode); 
    while $g(x,p)$ is the underlying physical equation for the system
    (e.g. the electromagnetic wave equation).

In contrast, the objective-first formulation is
    \begin{subequations}\label{eq:ob1}
    \begin{align} 
    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
    \end{align}
    \end{subequations}
    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
We term this formulation ``objective-first''
    because the design objective is prioritized even above satisfying physics;
    specifically, we force our design to always exhibit the desired performance
    ($f(x) = 0$), even at the expense of
    not perfectly satisfying the underlying physics which governs its operation.

@@

% How is it applied to waveguide coupler design?
\section{Objective-first design of arbitrary waveguide couplers}
We demonstrate the objective-first approach
    by designing waveguide couplers in two-dimensions.
Specifically, we work in the two-dimensional transverse electric mode,
    and choose $H_z$ as the field variable $x$,
    and $\epsilon^{-1}$ (the inverse of the permittivity) 
    as the structure variable $p$.
This results in the following form of the physics residual,
    \begin{equation}
    \|g(x,p)\|^2 = 
    \|g(H_z, \epsilon^{-1})\|^2 = 
    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
    \end{equation}
    where $\omega$ is the angular frequency,
    and $\mu_0$ is the permeability of free-space.

For the design objective, we choose a boundary-value formulation
    based on $H_z^\text{perfect}$,
    where $H_z^\text{perfect}$ is constructed 
    of the exact input and output waveguide modes at the input and output ports
    of the optimization region (where the coupler will be placed),
    repectively, and of zero-amplitude fields at the unused ports, 
    as illustrated in Fig.~\ref{fig:intro}.

@@

The mathematical form of the design objective is simply, 
    \begin{equation}
    f(H_z) = \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0.
    \end{equation}
That is to say,
    the values of $H_z$ and $\partial H_z / \partial n$
    (spatial derivative along normal direction)
    along the device boundary are forced to be 
    those of a device with perfect performance 
    (100\% coupling efficiency).

Such a design objective is both extremely simple and widely adaptable 
    to the design of nearly every kind of nanophotonic device.
Most importantly, it is trivial to enforce,
    requiring only that we overwrite boundary field values.
Our experience suggests that successful designs are possible for 
    arbitrary choice of relative phase between the input and output fields.

Finally, as in any method based on an objective-first approach,
    the physics residual is not guaranteed to decrease to zero.
Thus, it is entirely possible to never achieve 
    a physically realizable field, $H_z$.
In such cases, which are the norm rather than the exception,
    we find that a relatively small residual usually leads to
    fairly good, although imperfect, device performance.

The design problem is now
    \begin{subequations}\label{eq:act}
    \begin{align} 
    \text{decrease} & \quad  
        \| \nabla \times \epsilon^{-1} \nabla \times H_z - 
            \mu_0 \omega^2 H_z \|^2 \label{eq:act:obj} \\ 
    \text{subject to} & \quad 
        \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0.
    \end{align}
    \end{subequations}

This problem contains many local minima (it is non-convex\cite{boydbook});
    however, when either the field ($H_z$) or the structure ($\epsilon^{-1}$)
    variable is considered separately, Eq.~\ref{eq:act} has only one minimum
    (it is convex), and can be easily solved using standard methods
    such as employed in our previous work\cite{prevwork}.
We employ such an alternating directions strategy,
    where both $H_z$ and $\epsilon^{-1}$ are solved independently.
This process is extremely inefficient,
    but is employed because the underlying numerical methods
    do not need to be tuned by the user.
We expect considerable improvements in computational efficiency
    when more sophisticated algorithms are applied,
    especially those which can update $H_z$ and $\epsilon^{-1}$ independently.

Lastly, we limit the allowable values of $\epsilon$ to be between
    the permittivity of vacuum and of silicon,
    \begin{equation}
    \epsilon_0 \le \epsilon \le \epsilon_\text{silicon}.
    \end{equation}
A completely binary structure would be preferred,
    $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
    and will be pursued in a future work.
That said, the final designs presented here 
    all have significant portions which are already binary.

\subsection{Coupler designs}
We now present evidence that the method outlined above 
    is indeed able to design coupling structures between essentially
    any two nanophotonic waveguide modes.
To do so, we apply our method to the following five problems:
    \begin{enumerate}
    \item coupling between waveguides of different refractive index and width
        (Fig.~\ref{fig:fiber});
    \item coupling between waveguide modes of different order and symmetry
        (Fig.~\ref{fig:mode});
    \item coupling between waveguides that confine light 
        using different principles 
        (index guided vs. distributed Bragg reflection guided), 
        i.e., between a slab waveguide and a photonic crystal fiber
        (Fig.~\ref{fig:aircore})
    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
        waveguide (Fig.~\ref{fig:mim}); and
    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
        (Fig.~\ref{fig:wire}).
    \end{enumerate}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{1} 
    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
            a wide, low-index ($\epsilon=2.25$) waveguide. 
        The $H_z^\text{perfect}$ boundary values used as 
            the design objective are plotted in the upper-left quadrant, 
            the generated structure is shown in the upper-right quadrant, and
            the simulated $H_z$ fields of the device are shown 
            in the bottom two plots.
        The computed efficiency of the coupler is high, $98.2\%$, and
            the device is also extremely compact, 
            convering only $36 \times 66$ grid points,
            where the vacuum wavelength is 42 grid points.
        Computation time was 15 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{2} 
    \caption{Coupler that converts the fundamental waveguide mode to the
            second-order waveguide mode
            (a movie of the design progress is included as a
            supplementary material).
        This problem is quite difficult since the two modes are of 
            opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
            (which has the same dimensions and vacuum wavelength as 
            Fig.~\ref{fig:fiber})  
            with a coupling efficiency of $97.0\%$. 
        Computation time was 15 minutes on a personal computer.
        }
    \label{fig:mode}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{3}
    \caption{Coupler between a dielectric slab waveguide to 
            an air-core waveguide.
        Here, not only are the modes of opposite symmetry,
            but the output waveguide operates on a fundamentally different
            principle (distributed reflection) than the input waveguide 
            (index guided).
        The device still achieves an efficiency of $85.1\%$, demonstrating the
            versatility of our method.
        The vacuum wavelength is 25 grid points, 
            while the device footprint is still $36 \times 66$ grid points.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{4}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic metal-insulator-metal waveguide.
        The efficiency of the device is $92.9\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:mim}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{5}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic wire waveguide.
        The efficiency of the device is $93.2\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:wire}
\end{figure}

These results clearly demonstrate that our method can
    be applied to arbitrary input and output modes,
    as seen from the diverse selection of desired output waveguide modes.
Moreover, it produces highly efficient devices with  
    typical coupling efficiencies of $95\%$,
    which are at the same time compact 
    (with footprints of only 1-4 square vacuum wavelengths).
In addition, the method does not require a good initial guess for the design.
In our case the initial design was simply $\epsilon = 9$ everywhere
        (a somewhat arbitrary guess, other values work as well).
Finally, the method is computationally fast, 
    requiring only 15 minutes on a single-core personal computer.

These results form a key advancement in our understanding of 
    nanophotonic design; namely, 
    that it is indeed possible to efficiently design
    virtually any linear optical device using an objective-first approach.

\section{Conclusion}
We develop a fundamentally new approach to designing physical structures,
    which we term ``objective-first'', 
    in that we choose to satisfy the design objective 
    even above satisfying the physical equation which governs its operation.
We show that such an approach drastically reduces the
    amount of computation required per iteration, and 
    performs well even with a non-functional initial design.

We then apply an objective-first approach to the design of 
    five practical nanophotonic waveguide couplers which are difficult
    to solve with existing methods. 
We show that our method produces
    high-efficiency designs ($\sim 95\%$ efficiency) 
    in small footprints ($\sim 1$ square vacuum wavelength)
    between arbitrary waveguide modes.
Furthermore, out method
    is computationally fast (15 minutes on a single-core personal computer), and
    does not require trial-and-error, or even 
    a good starting design.\\

>>>>

\begin{thebibliography}{99}
\bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
    ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
    nanophotonic circuits,''
    Opt. Lett. \textbf{35}, 1290-1292 (2010)
\bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
    ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
    Opt. Lett. \textbf{26}, 1888-1890 (2001)
\bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
    ``Active control of slow light on a chip with photonic crystal waveguides,''
    Nature \textbf{438}, 65-69 (2005)
\bibitem{slotfocus} M. Lipson, 
    ``Guiding, Modulating, and Emitting Light on 
    Silicon-Challenges and Opportunities,'' 
    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005) 
\bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
    D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
    C. Lagahe, and R. Baets, 
    ``Electrically pumped InP-based microdisk lasers integrated with a 
    nanophotonic silicon-on-insulator waveguide circuit,'' 
    Opt. Express \textbf{15}, 6744-6749 (2007) 
\bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
    D. S. Ly-Gagnon, K. C. Saraswat and D. A. B. Miller, 
    ``Nanometre-Scale Germanium Photodetector Enhanced by a 
    Near-Infrared Dipole Antenna,'' 
    Nature Photonics \textbf{2}, 226 – 229 (2008) 
% \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
%     ``Nanotaper for compact mode conversion,'' 
%     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
%     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
%     ``Adiabatic theorem and continuous coupled-mode theory for 
%     efficient taper transitions in photonic crystals,''
%     Phys. Rev. E \textbf{66}, 066608 (2002)
% \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
%     ``Robust topology optimization of photonic crystal waveguides with 
%     tailored dispersion properties.'' 
%     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
%     \emph{Convex Optimization} 
%     (Cambridge University Press, 2004)
\bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10570 (2011) 
\bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

% Why is waveguide mode conversion important?
Optical mode conversion, 
    the efficient transfer of photons from one guided mode to another,
    is a fundamental requirement in nanophotonics.
For instance, efficient conversion between waveguides modes
    is essential for:
    \begin{itemize}
        \item Coupling to and from optical fiber\cite{fibergrating}, 
        to communicate with the outside world.
    \item Coupling between various nanophotonic waveguides, 
        since different waveguides are best suited for different applications.
        For example, ridge waveguides seem ideal for 
            low-loss transport\cite{ridge},
            but other waveguides, 
            such as photonic crystal waveguides or slot waveguides,
            may be better suited for slow-light\cite{pcslow} 
            or nonlinear optical devices based on 
            localized field intensities\cite{slotfocus}.
    \item Coupling between different materials systems such as
       passive, active\cite{active}, and metallic\cite{metallic} devices. 
    \end{itemize}
In fact, the problem of converting between nanophotonic modes is essentially
    the function of all linear nanophotonic devices, since
    any linear device is completely characterized by its input and output modes
    and the coupling coefficients between them.

In this paper, we present a method to solve the problem 
    of designing linear nanophotonic devices.
We then demonstrate this method by designing coupling structures 
    between various nanophotonic waveguides.
Furthermore, we show that our method 
     does not require a good initial design,
     is computationally fast,
     and can generate high efficiency couplers within a very small footprint. 
% 
% 
% % Why are current solutions insufficient?
% % Brute force
% Of the design strategies currently available,
%     brute-force parameter search is the most often employed 
%     because of its sheer simplicity.
% Although it may be suitable for tuning existing designs,
%     the parameter space for most practical devices is simply too large
%     for such a strategy to be tractable.
% 
% % Adiabatic mode conversion (large devices, symmetry breaking)
% Adiabatic mode conversion strategies have been succesful
%     for certain fiber-waveguide\cite{fwadia} and 
%     waveguide-waveguide\cite{wwadia} couplers,
%     even if the resulting devices often require large footprints.
% However, adiabatic approaches cannot be used in many important cases 
%     such as coupling in the out-of-plane direction, or
%     coupling between modes of opposite symmetry.

% How does your algorithm solve this problem?
% \subsection{Advantages of objective-first design}
\section{Objective-first approach}
% What is objective-first optimization?
Physical structures are typically designed by solving the following problem:
    \begin{subequations}\label{eq:adj}
    \begin{align} 
    \text{decrease} & \quad f(x) \label{eq:adj:obj} \\ 
    \text{subject to} & \quad g(x,p) = 0, \label{eq:adj:con}
    \end{align}
    \end{subequations}
    where $x$ is the field variable and $p$ is the structure variable.
Here, $f(x)$, the \emph{design objective}, 
    calculates the performance of the device 
    (e.g. amount of power lost); 
    while $g(x,p)$ is the underlying physical equation for the system
    (e.g. the electromagnetic wave equation).

In contrast, the objective-first approach solves 
    \begin{subequations}\label{eq:ob1}
    \begin{align} 
    \text{decrease} & \quad \|g(x,p)\|^2 \label{eq:ob1:obj} \\ 
    \text{subject to} & \quad f(x) = 0, \label{eq:ob1:con}
    \end{align}
    \end{subequations}
    where $\|g(x,p)\|^2$ is the \emph{physics residual}.
We term this formulation ``objective-first''
    because the design objective is prioritized even above satisfying physics;
    specifically, we force our design to always exhibit the desired performance
    ($f(x) = 0$), even at the expense of
    not perfectly satisfying the underlying physics which governs its operation.

@@

% How is it applied to waveguide coupler design?
\section{Objective-first design of waveguide couplers}
We now demonstrate the objective-first approach
    by designing waveguide couplers in two-dimensions.
Specifically, we work in the two-dimensional transverse electric mode,
    choosing $H_z$ as the field variable $x$,
    and $\epsilon^{-1}$ (the inverse of the permittivity) 
    as the structure variable $p$.
This results in the following form of the physics residual,
    \begin{equation}
    \|g(x,p)\|^2 = 
    \|g(H_z, \epsilon^{-1})\|^2 = 
    \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
    \end{equation}
    where $\omega$ is the angular frequency,
    and $\mu_0$ is the permeability of free-space.

In order to produce a method applicable 
    to the design of any linear nanophotonic device,
    we note that its performance
    will be completely characterized by the fields along its boundary,
    and therefore, 
    we choose a boundary-value formulation for the design objective.
Namely, we first compute the boundary fields needed to obtain
    perfect performance, $H_z^\text{perfect}$,
    and then form the design objective as
    \begin{equation}
    f(x) = f(H_z) = \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0,
    \end{equation}
    where $\partial H_z / \partial n$ 
    denotes the spatial derivative in the direction normal to the boundary.

@@

Such a design objective is both extremely simple and widely adaptable 
    to the design of any linear nanophotonic device.
Additionally, it is trivial to enforce,
    often requiring only that we overwrite boundary field values.
On the other hand, such a formulation often prohibits the physics residual 
    from disappearing completely; 
    however, we find that very good device performance is still obtained
    as long as the physics residual is sufficiently small.

Lastly, we employ an alternating directions strategy,
    where both $x$ and $p$ are solved iteratively\cite{prevwork}
    and limit the allowable values of $\epsilon$ to be between
    the permittivity of vacuum and of silicon,
    \begin{equation}
    \epsilon_0 \le \epsilon \le \epsilon_\text{silicon}.
    \end{equation}
Note that a completely binary structure,
    where $\epsilon = \{\epsilon_0, \epsilon_\text{silicon}\}$,
    is needed for manufacturing purposes; this will be pursued in a future work.
That said, the final designs presented here 
    all have significant portions which are already binary.

\subsection{Coupler designs}
We now present five results which suggest our method
    is indeed able to design arbitrary linear nanophotonic devices.
These results comprise of couplers between 
    the following nanophotonic waveguides:
    \begin{enumerate}
    \item coupling between waveguides of different refractive index and width
        (Fig.~\ref{fig:fiber});
    \item coupling between waveguide modes of different order and symmetry
        (Fig.~\ref{fig:mode});
    \item coupling between waveguides that confine light 
        using different principles 
        (index guided vs. distributed Bragg reflection guided), 
        i.e., between a slab waveguide and a photonic crystal fiber
        (Fig.~\ref{fig:aircore})
    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
        waveguide (Fig.~\ref{fig:mim}); and
    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
        (Fig.~\ref{fig:wire}).
    \end{enumerate}
All the designs presented are both highly efficient 
    ($\sim 95\%$ coupling efficiency)
    and extremely compact 
    (with footprints of only 1-4 square vacuum wavelengths).
In addition, good starting points were not required; 
    all initial designs were simply $\epsilon = 9$ everywhere
    (a somewhat arbitrary guess, other values work as well).
Finally, only 15 minutes on a single-core personal computer
    were needed to obtain each design.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{1} 
    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
            a wide, low-index ($\epsilon=2.25$) waveguide. 
        The $H_z^\text{perfect}$ boundary values used as 
            the design objective are shown in the upper-left plots, 
            the generated structure is shown in the upper-right plot, and
            the simulated $H_z$ fields of the device are shown 
            in the bottom two plots.
        The computed efficiency of the coupler is high, $98.2\%$, and
            the device is also extremely compact, 
            convering only $36 \times 66$ grid points,
            where the vacuum wavelength is 42 grid points.
        Computation time was 15 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{2} 
    \caption{Coupler that converts the fundamental waveguide mode to the
            second-order waveguide mode
            (a movie of the design progress is included as a
            supplementary material).
        This problem is quite difficult since the two modes are of 
            opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
            (which has the same dimensions and vacuum wavelength as 
            Fig.~\ref{fig:fiber})  
            with a coupling efficiency of $97.0\%$. 
        Computation time was 15 minutes on a personal computer.
        }
    \label{fig:mode}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{3}
    \caption{Coupler between a dielectric slab waveguide to 
            an air-core waveguide.
        Here, not only are the modes of opposite symmetry,
            but the output waveguide operates on a fundamentally different
            principle (distributed reflection) than the input waveguide 
            (index guided).
        The device still achieves an efficiency of $85.1\%$, demonstrating the
            versatility of our method.
        The vacuum wavelength is 25 grid points, 
            while the device footprint is still $36 \times 66$ grid points.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{4}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic metal-insulator-metal waveguide.
        The efficiency of the device is $92.9\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:mim}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{5}
    \caption{Coupler between a dielectric slab waveguide to 
            a plasmonic wire waveguide.
        The efficiency of the device is $93.2\%$ and 
            has the same wavelength and footprint as the device in
            Fig.~\ref{fig:aircore}.
        Computation time was 15 minutes on a personal computer.
        }
        \label{fig:wire}
\end{figure}

\section{Conclusion}
We develop a fundamentally new approach to designing physical structures,
    which we term ``objective-first'', 
    in that we choose to satisfy the design objective 
    even above satisfying the physical equation which governs its operation.
We then apply this approach to the design of 
    various nanophotonic waveguide couplers,
    and show that our method produces
    high-efficiency designs ($\sim 95\%$ efficiency) 
    in small footprints (1-4 square vacuum wavelengths)
    without needing a good starting point.
Furthermore, we suggest that such a methodology may be applicable
    to the design of any linear nanophotonic device.\\
